Bayesian Hyper-Heuristics

### 2023-02-01 article/sections/08-results.tex
🚧 (article): Save point, WIP

Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results. The \acs{BHH} applies a form of \index{online learning}online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs. The number of training steps executed is dependent on the batch size applied for each dataset.

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur within the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.

@@

Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

@@

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.

@@

From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

This section provides a detailed investigation into the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probabilistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.

Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Indices 0, 6, 7, and 8 represent the distribution of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$. Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:thetas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:thetas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:thetas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
		\label{fig:results:case_study:thetas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:thetas}
\end{figure}

From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modelling.

Towards the end of the training process, the \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process. Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process. As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.

@@

Another observation to make occurs in the first 30 steps of the training process. In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.

It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps. As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics. Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.

Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected \index{heuristic}heuristic selection probabilities of 0.1. This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations. This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.

Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration. This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from. A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the \index{heuristic}heuristic selection probabilities. Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.

@@

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$. As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.

Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:p_H:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:p_H:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:p_H:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
		\label{fig:results:case_study:p_H:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8. The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H}
\end{figure}

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances. Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concluded that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}. Furthermore, the prior \index{heuristic}heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.

@@

This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}. These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}. The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of \index{heuristic}heuristic selection probabilities and the entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.

Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs. Similar to before, these illustrations are also presented in log scale. As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
		\label{fig:results:case_study:p_HgEC:0:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
		\label{fig:results:case_study:p_HgEC:0:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
		\label{fig:results:case_study:p_HgEC:0:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
		\label{fig:results:case_study:p_HgEC:0:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0}
\end{figure}

>>>>

Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results. The \acs{BHH} applies a form of online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs. The number of training steps executed is dependent on the batch size applied for each dataset.

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur within the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.

@@

Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

@@

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.

@@

From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}. Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves. The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.

Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$. Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:thetas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:thetas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:thetas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
		\label{fig:results:case_study:thetas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:thetas}
\end{figure}

From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.

Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics. This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process. Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process. As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.

@@

Another observation to make occurs in the first 30 steps of the training process. In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.

It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps. As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing heuristics. Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.

Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1. This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations. This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.

Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration. This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from. A small reanalysis interval and a small replay window size allows for more exploration of the heuristic space, but can also yield greater variance of the heuristic selection probabilities. Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.

@@

This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$. As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.

Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:p_H:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:p_H:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:p_H:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
		\label{fig:results:case_study:p_H:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8. The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H}
\end{figure}

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of heuristic performances. Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}. Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.

@@

This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}. These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}. The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.

Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs. Similar to before, these illustrations are also presented in log scale. As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
		\label{fig:results:case_study:p_HgEC:0:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
		\label{fig:results:case_study:p_HgEC:0:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
		\label{fig:results:case_study:p_HgEC:0:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
		\label{fig:results:case_study:p_HgEC:0:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy. The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0}
\end{figure}
